Light Transport Techniques for Tensor Field Visualization

### 2019-08-01 beamer2thesis/dummy.tex
update

\frame{
\frametitle{{Tensor Fields - Tensor Field Lines}}

\begin{columns}
\begin{column}{.6\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Procedure}}
follow major/minor eigenvectors along pathlines
\end{block}
\end{small}
\bigskip
\begin{small}
\begin{itemize}
	\item ambiguity for nearly isotropic cases:\\ small changes in components effect large changes in tensor field line orientation (see Fig.)
	\item therefore susceptive to noise in data
	\item trajectories can cross each other\\
	$\Rightarrow$ effects erroneous trajectories, hard to interpret
\end{itemize}
\end{small}

\end{column}
\begin{column}{.4\textwidth}
\centering
\begin{figure}[t]
\centering
\includegraphics[height=0.8\textwidth]{nearly_isotropic.pdf}
\caption*{Ambiguity}
\end{figure}

\end{column}
\end{columns}
} % END OF FRAME

>>>>

\frame{
\frametitle{{Propagation Scheme - Physical Models}}
\begin{itemize}
	\item phase function model from Rayleigh scattering:
\begin{block}{\centering \textbf{Phase Functions\footnote[frame]{\url{http://www.met.reading.ac.uk/~jp902366/rad/phase_function_report.pdf}\bigskip}}}
	\begin{align*}
 	P(\omega) &= \frac{T(\omega)}{\int_{k\pi}^{(k+1)\pi}T(\omega)\mathop{d\omega}}\\
 	\mathit{with} \int_0^{\pi} P(\omega) &= 1.
	\end{align*}
\end{block}
	\item each tensor is then a unique footprint: $t_{i,j}\mapsto T(\omega)$
\end{itemize}

} % END OF FRAME

\frame{
\frametitle{{Propagation Scheme - Physical Models}}
\begin{itemize}
	\item crystal lattices reveal refractive indices dependent on direction, which lead to anisotropic light transport inside the medium (birefringence: e.g. quartz, ruby):
\begin{block}{\centering \textbf{Indicatrix\footnote[frame]{\url{http://edafologia.ugr.es/optmine/intro/indicatw.htm}} - Refractive Ellipsoid}}
	\begin{align*}
	T(\omega) = \frac{ab}{\sqrt{a^{2}\sin^{2}(\omega)+b^{2}\cos^{2}(\omega)}} =\frac{n_1n_2}{\sqrt{n_1^2\sin^2(\omega)+n_2^2\cos^2(\omega)}}
\end{align*}
\end{block}\bigskip
	\item each tensor is then a unique footprint: $t_{i,j}\mapsto T(\omega)$
\end{itemize}

} % END OF FRAME
